---
title: 
author: "MA615"
date: "2021-Nov-17"
output:
  revealjs::revealjs_presentation:
    theme: solarized
    highlight: pygments
    template: hw_temp_1.html
    css: reveal.css
    center: false
    transition: slide
---
# sentiment analysis

```{r  echo=FALSE, fig.align='center', fig.height=5, fig.width= 4}
library(png)
library(jpeg)
library(grid)

img = readJPEG("JaneAusten1810.jpg")
grid.raster(img)

```

```{r setup, include=FALSE}

suppressPackageStartupMessages(
  library(tidyverse))

  library(scales)
  library(methods)
  library(knitr)
  library(kableExtra)

  library(janeaustenr)
  library(dplyr)
  library(stringr)

  library(tidytext)
  library(gutenbergr)

  library(scales)
  
  opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  cache = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = TRUE,
  dpi = 300,
  cache.lazy = FALSE,
  tidy = "styler",
  out.width = "90%",
  fig.align = "center",
  fig.width = 5,
  fig.height = 7
)

  options(crayon.enabled = FALSE)

  theme_set(theme_light())

```

# sentiment analysis
```{r  echo=FALSE, fig.align='center', fig.height=1.5}
library(png)
library(grid)

img = readPNG("fig2-1.png")
grid.raster(img)

```

<div style="font-size:18pt">

Unigram lexicons attempt to reduce single words to sentiment categories.

<h5>AFINN:  Finn Årup Nielsen  </h5>
Assigns words with a score between -5 and 5.

<h5>bing:   Bing Liu et al.  </h5>
Categorizes words as positive or negative.  

<h5>nrc:    Saif Mohammad and Peter Turney  </h5>
Uses binary yes/no score in categories of positive, negative, anger, anticipation, disgust, fear, joy, sadness, surprise, and trust.  



## For example: afinn
<div style="font-size:12pt; font-weight: bold">
```{r}

get_sentiments("afinn")

```
</div>




## For example: nrc  
<div style="font-size:12pt; font-weight: bold">
```{r}
get_sentiments("nrc")
```

</div>

# Sentiment analysis of Jane Auten's Emma

<div style="font-size:12pt; font-weight: bold">

```{r echo=FALSE}

tidy_books <- austen_books() %>%
  group_by(book) %>%
  mutate(
    linenumber = row_number(),
    chapter = cumsum(str_detect(text, 
                                regex("^chapter [\\divxlc]", 
                                      ignore_case = TRUE)))) %>%
  ungroup() %>%
  unnest_tokens(word, text)

```


```{r}
nrc_joy <- get_sentiments("nrc") %>% 
  filter(sentiment == "joy")

tidy_books %>%
  filter(book == "Emma") %>%
  inner_join(nrc_joy) %>%
  count(word, sort = TRUE)

```
</div>



# Visualization of sentiments 

<div style="font-size:12pt">

```{r echo = FALSE}
jane_austen_sentiment <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(book, index = linenumber %/% 80, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)
```



```{r echo = FALSE, fig.height=3}
ggplot(jane_austen_sentiment, aes(index, sentiment, fill = book)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~book, ncol = 2, scales = "free_x")
```

</div>

# Comparing lexicons with Pride & Prejudice

<div style="font-size:12pt">


```{r echo=FALSE}
pride_prejudice <- tidy_books %>% 
  filter(book == "Pride & Prejudice")

#pride_prejudice
```


```{r echo=FALSE}
afinn <- pride_prejudice %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(index = linenumber %/% 80) %>% 
  summarise(sentiment = sum(value)) %>% 
  mutate(method = "AFINN")

bing_and_nrc <- bind_rows(
  pride_prejudice %>% 
    inner_join(get_sentiments("bing")) %>%
    mutate(method = "Bing et al."),
  pride_prejudice %>% 
    inner_join(get_sentiments("nrc") %>% 
                 filter(sentiment %in% c("positive", 
                                         "negative"))
    ) %>%
    mutate(method = "NRC")) %>%
  count(method, index = linenumber %/% 80, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)
```





```{r echo=FALSE, fig.height=3}
bind_rows(afinn, 
          bing_and_nrc) %>%
  ggplot(aes(index, sentiment, fill = method)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~method, ncol = 1, scales = "free_y")
```










# word cloud

<div style="font-size:12pt">

```{r fig.height=2.5}
library(wordcloud)

tidy_books %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))
```
</div>

## One more cloud

<div style="font-size:12pt">

```{r echo=FALSE}
library(reshape2)
```

```{r fig.height=2.3}
tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("gray20", "gray80"),
                   max.words = 100)
```

</div>

